---
title: "Base RAIS"
author: "Tainá Rocha"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Acessando dados RAIS
 
Vamos utilizar o [datalake da inciativa base dados](https://basedosdados.org/) 


#### 1. Get the dataset

I obtained the data from SCOPUS and Web of Science repositories (WOS). I searched for articles using a generic query for test purposes. It is important to emphasize that building a correct query requires [some steps](https://guides.library.illinois.edu/c.php?g=980380&p=7089538)  



Usando o robo

```{r warning=FALSE}
library(bigrquery)
library(dplyr)

conection <- dbConnect(
  bigquery(),
  project = "basedosdados",
  dataset = "br_me_rais",
  billing = "Semana Data Science" # Google Cloud Project 
)
conection
```





Abixo está o código que carrega as primeiras 5 linhas de microdados 
 
Ler de um arquivo 
```{r}
tabela_normal <- read.csv("https://raw.githubusercontent.com/curso-r/main-r4ds-1/master/dados/imdb.csv")

head(tabela_normal)

```

